Title here

### 2017-01-02 portfolio/text/ms.Rmd
Strip whitespace and edit discussion

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provides substantial
benefits over strategies with lower diversity [REFS]. However, the ability of
individuals to effectively diversify is limited by regulation and market forces
in practice. Here we document the effect of changing species diversity on
revenue and revenue variability across three scale. Each scale reflects
individual-level choices that can affect species diversity. We find that
individuals with fishing permit sets that allow high levels of species diversity
tend to have lower revenue variability. Adding a fisheries permit usually
increases revenue and decreases revenue variability. Within the constraints of
a permit and accounting for effort, specializing (reducing species diversity)
tends to increase revenue while both specializing or generalizing tends to be
associated with greater revenue variability - though there are considerable
differences among fisheries. Thus, the most effective mechanism by which species
diversity can lower revenue variability for individual fishers --- switching or
adding fishing permits --- is costly, limited by regulations, and consequently
unavailable to many individuals in practice.

Our findings across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014], but we also found that within
strategies, for individuals, specializing tended to be associated with increased
revenue and altering species diversity tended to be associated with increased
revenue variability. Specializing has been shown to be profitable in some
circumstances for other natural resource sectors. For example, while
diversification is generally helpful for small-scale farmers, farmers that
specialize on high-demand and high-value crops such as tobacco or cocoa can
benefit, at least in the short term, from specializing on these crops (REF). In
terms of variance, there are number of reasons by annual revenue variability
might be expected to increase with changes to individual fished species
diversity. First, changes to fishing patterns will sometimes be associated with
a learning or adaptation phase as individuals become accustomed to new
locations, new gear, or new species. Secondly, changes in diversity might
reflect years in which targeted species were less available and fishers were
forced to target other species or landed more bycatch. Most importantly, this
increased variability technically reflects an inability for our large-scale
model to predict an individual's revenue in a subsequent year. There are many
reasons, often unique to an individual permit holder and therefore not included
in a large-scale model, that might make that specific individual's revenue less
predictable given a change in species diversity compared to not changing species
diversity from one year to the next.

@@

External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate (REF), it is particularly important that individuals who rely
on natural resources as a primary source of income have strategies to reduce
risk. Though variability in individual revenues may not be actively incorporated
into many management decisions, analyses like ours help to understand the range
of diversification strategies available and how their benefits may change over
time.

@@

<!-- vim: textwidth=80 
-->

>>>>

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provides substantial
benefits over strategies with lower diversity [REFS]. However, in practice, the
ability of individuals to effectively diversify is limited by regulation and
market forces. Here we document the effect of individual-level changes in
species diversity on revenue and revenue variability across three scales. We
find that (1) individuals with fishing permit sets that allow high levels of
species diversity tend to have lower revenue variability. (2) Adding a fisheries
permit usually increases revenue and decreases revenue variability. However, (3)
within the constraints of a permit and accounting for effort, specializing tends
to increase revenue while both specializing and generalizing tend to correlate
with greater revenue variability with considerable differences amongst
fisheries. Thus, the most effective mechanism by which species diversity can
lower revenue variability for individual fishers --- switching or adding fishing
permits --- is costly, limited by regulations, and consequently unavailable to
many individuals.

Our findings across fishing strategies are in line with previous findings
[@kasperski2013, @sethi2012b, @sethi2014], but we also found that within
strategies, for individuals, specializing tended to be associated with increased
revenue and altering species diversity tended to be associated with increased
revenue variability. Specializing has been shown to be profitable in some
circumstances for other natural resource sectors. For example, while
diversification is generally helpful for small-scale farmers, farmers that
specialize on high-demand and high-value crops such as tobacco or cocoa can
benefit, at least in the short term, from specializing (REF). In terms of
variance, there are number of reasons by annual revenue variability might
increase with changes to individual fished species diversity. First, changes to
fishing patterns will sometimes be associated with a learning or adaptation
phase as individuals become accustomed to new locations, new gear, or new
species. Secondly, changes in diversity might reflect years in which targeted
species were less available and fishers were forced to target other species or
landed more bycatch. Most importantly, this increased variability technically
reflects an inability for our large-scale model to predict an individual's
revenue in a subsequent year. There are many reasons, often unique to an
individual permit holder and therefore not included in a large-scale model, that
might make that specific individual's revenue less predictable if species
diversity changes.

@@

External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate (REF), it is particularly important that individuals who rely
on natural resources as a primary source of income have strategies to reduce
risk. Though variability in individual revenue may not be actively incorporated
into many management decisions, analyses like ours help to understand the range
of diversification strategies available and how their benefits may change over
time.

@@

<!-- vim: textwidth=80

-->
